---
title: "BeachTan Inc. Analytics Workflow"
author: "Abby Farrell"
date: "October 2, 2020"
output: html_document
code_folding: hide
---

The goal of the following analysis is to aid the Marketing Team of Beach Tan Inc. in understanding factors that contribute to a customer's likelihood of spending money in upgrade revenue within the company. I am performaning an analysis on the customer data provided by Beach Tan to explain any correlation to upgrade revenue found.

# 1 Loading & Cleaning Data

The chunk below includes installing packages needed for the following analysis, as well as any recoding done to ensure accurate results. The output shows a summary of the variables after the data has been prepped, as well as a plot introducing the data.

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r echo=FALSE}
library(pacman)
p_load(tidyverse, dplyr, plyr, DataExplorer, corrplot)
setwd("/Users/abbyfarrell/Documents/ISA 616/Beach Tan Project Files")
df<-read.csv("BeachTan.csv", stringsAsFactors = TRUE)

#recode as factors
df$UIDStoreLocation <- as.factor(df$UIDStoreLocation)
df$MembershipType <- as.factor(df$MembershipType)
df$MembershipLevel <- as.factor(df$MembershipLevel)
levels(df$MembershipType) <-c('Non Membership', 'Monthly Membership', 'Annual Membership')
levels(df$MembershipLevel) <-c('Non Membership', 'Fast', 'Faster', 'Fastest', 'Instant')
df$Gender = fct_recode(df$Gender, 'Missing' = "", 'Missing' = "#NULL!")

summary(df)
plot_intro (df)
```

# 2 Correlation

As seen above, we have a relatively straight-forward data set with no missing values. This will allow us to now examine any correlation between the given variables (first integers, then factors) and the upgrade revenue specifically.

```{r echo=FALSE}
#Find correlation in variables
correlation <- unlist(lapply(df, is.numeric))
dfcorr<-df[,correlation]
M<-cor(dfcorr, use = "complete.obs")
corrplot(M, method='circle')

plot(df$UpgradeRevenue, df$MembershipType)
plot(df$UpgradeRevenue, df$MembershipLevel)
plot(df$UpgradeRevenue, df$Gender)
plot(df$UpgradeRevenue, df$UIDStoreLocation)
```
There are a couple observations we can make from the graphs above. 
