---
title: "BeachTan Inc. Analytics Workflow"
author: "Abby Farrell"
date: "October 2, 2020"
output: html_document
code_folding: hide
---

The goal of the following analysis is to aid the Marketing Team of Beach Tan Inc. in understanding factors that contribute to a customer's likelihood of spending money in upgrade revenue within the company. I am performaning an analysis on the customer data provided by Beach Tan to explain any correlation to upgrade revenue found.

# 1 Loading & Cleaning Data

The chunk below includes installing packages needed for the following analysis, as well as any recoding done to ensure accurate results. The output shows a summary of the variables after the data has been prepped, as well as a plot introducing the data.

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r echo=FALSE}
library(pacman)
p_load(tidyverse, dplyr, plyr, DataExplorer, corrplot)
setwd("/Users/abbyfarrell/Documents/ISA 616/Beach Tan Project Files")
df<-read.csv("BeachTan.csv", stringsAsFactors = TRUE)

#recode as factors
df$UIDStoreLocation <- as.factor(df$UIDStoreLocation)
df$MembershipType <- as.factor(df$MembershipType)
df$MembershipLevel <- as.factor(df$MembershipLevel)
levels(df$MembershipType) <-c('Non Membership', 'Monthly Membership', 'Annual Membership')
levels(df$MembershipLevel) <-c('Non Membership', 'Fast', 'Faster', 'Fastest', 'Instant')
df$Gender = fct_recode(df$Gender, 'Missing' = "", 'Missing' = "#NULL!")

summary(df)
plot_intro (df)
```

# 2 Correlation

As seen above, we have a relatively straight-forward data set with no missing values. This will allow us to now examine any correlation between the given variables (first integers, then factors) and the upgrade revenue specifically.

```{r echo=FALSE}
#Find correlation in variables
correlation <- unlist(lapply(df, is.numeric))
dfcorr<-df[,correlation]
M<-cor(dfcorr, use = "complete.obs")
corrplot(M, method='circle')

plot(df$UpgradeRevenue, df$MembershipType, main="Membership Type vs. Upgrade Rev", xlab = "Upgrade Revenue", ylab= "Membership Type", col="red")
plot(df$UpgradeRevenue, df$MembershipLevel, main="Membership Level vs. Upgrade Rev", xlab = "Upgrade Revenue", ylab= "Membership Level", col="blue")
plot(df$UpgradeRevenue, df$Gender, main="Gender vs. Upgrade Rev", xlab = "Upgrade Revenue", ylab= "Gender", col="green")
plot(df$UpgradeRevenue, df$UIDStoreLocation, main="Store Location vs. Upgrade Rev", xlab = "Upgrade Revenue", ylab= "Store Location", col="orange")
```

There are a couple observations we can make from the graphs above. First, looking at the correlation plot of the numeric variables we can see that upgrade revenue has the strongest correlation with UV Tans (Sunless Tans second). The scatter plots showing the different factors against our target variable tells us which membership type and level contributed most to upgrade revenue.
